dynamics

### 2023-06-05 scripts/workshop/dynamics.Rmd
trying out no demo changes

@@

output_a1 %<>% mutate(I = Ia+Ib)
output_c1 %<>% mutate(I = Ia+Ib)
output_h1 %<>% mutate(I = Ia+Ib)
output_n1 %<>% mutate(I = Ia+Ib)
output_x1 %<>% mutate(I = Ia+Ib)
output_x2 %<>% mutate(I = Ia+Ib)
output_x3 %<>% mutate(I = Ia+Ib)
output_x4 %<>% mutate(I = Ia+Ib)

output_a1 %<>% mutate(X = I + V)
output_c1 %<>% mutate(X = I + V)
output_h1 %<>% mutate(X = I + V)
output_n1 %<>% mutate(X = I + V)
output_x1 %<>% mutate(X = I + V)
output_x2 %<>% mutate(X = I + V)
output_x3 %<>% mutate(X = I + V)
output_x4 %<>% mutate(X = I + V)
```

>>>>

```{r}
params_c1 <- c(mu_a=1/45,
          mu_b=1/45,
          beta=spec_1,
          betab=spec_2,
          phi=env_rate,
          lambda=5/3,
          alpha=1/10,
          sigma=1/2,
          epsilon=1/1.947799)  # model parameters

xstart_c1 <- c(Sa=100,
          Ia=1,
          Ra=0,
          Sb=50,
          Ib=1,
          Rb=0,
          V=0)  # initial conditions

output_c2 <- as.data.frame(lsoda(xstart_c1,times,rm1,params_c1)) # tells computer to solve (integrate) equations
```

@@

output_a1 %<>% mutate(I = Ia+Ib)
output_c1 %<>% mutate(I = Ia+Ib)
output_c2 %<>% mutate(I = Ia+Ib)
output_h1 %<>% mutate(I = Ia+Ib)
output_n1 %<>% mutate(I = Ia+Ib)
output_x1 %<>% mutate(I = Ia+Ib)
output_x2 %<>% mutate(I = Ia+Ib)
output_x3 %<>% mutate(I = Ia+Ib)
output_x4 %<>% mutate(I = Ia+Ib)

output_a1 %<>% mutate(X = I + V)
output_c1 %<>% mutate(X = I + V)
output_c2 %<>% mutate(X = I + V)
output_h1 %<>% mutate(X = I + V)
output_n1 %<>% mutate(X = I + V)
output_x1 %<>% mutate(X = I + V)
output_x2 %<>% mutate(X = I + V)
output_x3 %<>% mutate(X = I + V)
output_x4 %<>% mutate(X = I + V)
```
